Fig2: Candidate genes

### 2020-04-23 analysis/figure-2.Rmd
new fig 2

a1 <- candidateboxplot("hypothalamus", hypDEGs, "female") + labs(x = NULL, title = "hypothalamus") 
a2 <- candidateboxplot("hypothalamus", hypDEGs, "male") + labs(x = NULL) +
  theme(strip.text = element_blank())

b1 <- candidateboxplot("pituitary", pitDEGs, "female") + labs(x = NULL, title = "pituitary")
b2 <- candidateboxplot("pituitary", pitDEGs, "male") + labs(x = NULL) +
  theme(strip.text = element_blank())

c1 <- candidateboxplot("gonad", gonadDEGs, "female") + labs(x = NULL, title = "gonad")
c2 <- candidateboxplot("gonad", gonadDEGs, "male") + 
  theme(strip.text = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot_grid(a1,a2, b1,b2, c1,c2, nrow = 6, labels = c("A", " ","B", " ", "C", " "), label_size = 8,
          rel_heights = c(1, 0.75, 1, 0.75, 1, 1))
```

>>>>

a1 <- candidateboxplot("hypothalamus", hypDEGs, "female") + labs(x = NULL, title = "hypothalamus")

b1 <- candidateboxplot("pituitary", pitDEGs, "female") + labs(x = NULL, title = "pituitary")

b2 <- candidateboxplot("pituitary", "PRL", "male") + labs(x = NULL, y = NULL,  title = "pituitary")

b12 <- plot_grid(b1,b2,nrow = 1, labels = c("B", "C"),
          label_size = 8, rel_widths = c(4,1))

c1 <- candidateboxplot("gonad", gonadDEGs, "female") + 
  labs(x = NULL, title = "gonad")

plot_grid(a1, b12, c1, nrow = 3, labels = c("A", " ","D"), 
          label_size = 8)
```
